Adversarial Training of Neural Networks\\ against Systematic Uncertainty

### 2016-08-31 tex/paper.tex
save
added note for continuous case

Adversarial training was first proposed by \cite{goodfellow2014generative} as a
way to build a generative model capable of producing samples from random noise
$z \sim p_Z$. More specifically, the authors pit a generative model $g: {\cal Z}
\mapsto \mathbb{R}^p$ against an adversary classifier $d : \mathbb{R}^p \mapsto \{
0, 1\}$ whose antagonistic objective is to recognize real data $X$ from generated data $g(Z)$. Both
models $g$ and $d$ are trained simultaneously, in such a way that $g$ learns to
produce samples that are difficult to identify by $d$, while $d$ incrementally
adapts to changes in $g$. At the equilibrium, $g$ models a distribution whose
samples can be identified by $d$ only by chance. That is, assuming enough
capacity in $d$ and  $g$, the distribution $p_{g(Z)}$ eventually converges
towards the real distribution $p_X$.

@@

>>>>

Adversarial training was first proposed by \cite{goodfellow2014generative} as a
way to build a generative model capable of producing samples from random noise
$z \sim p_Z$. More specifically, the authors pit a generative model $g: \mathbb{R}
\mapsto \mathbb{R}^p$ against an adversary classifier $d : \mathbb{R}^p \mapsto \{
0, 1\}$ whose antagonistic objective is to recognize real data $X$ from generated data $g(Z)$. Both
models $g$ and $d$ are trained simultaneously, in such a way that $g$ learns to
produce samples that are difficult to identify by $d$, while $d$ incrementally
adapts to changes in $g$. At the equilibrium, $g$ models a distribution whose
samples can be identified by $d$ only by chance. That is, assuming enough
capacity in $d$ and  $g$, the distribution $p_{g(Z)}$ eventually converges
towards the real distribution $p_X$.

@@

\glnote{Extension to continuous nuisance parameters: have the adversary $r$
models the conditional distribution $p(z|f(X;\theta_f))$, e.g. with network
whose 2 outputs are parameters of a truncated gaussian and optimized such that
$p(z|f(X;\theta_f)) \approx N(\mu(f(X;\theta_f);\theta_r), \sigma(f(X;\theta_f);
\theta_r)$. The associated loss can be the likelihood (or?), which is maximal when the
approximation is perfect and minimal when the truncated gaussian degenerates to
a uniform (when $\sigma$ is large), in which case we should have the guarantee
that $f$ is pivotal.}
